---
output: 
    html_document:
        keep_md: true
---

#PA1_template.Rmd
##mbieganski
##27 marca 2016

1. Code for reading in the dataset and/or processing the data

```{r}
nadf <- read.csv("activity.csv")
df <- nadf[complete.cases(nadf$steps),]
```

2. Histogram of the total number of steps taken each day

```{r}
library(ggplot2)

sumdf <- aggregate(df$steps, by=list(date=df$date), FUN=sum)
meandf <- aggregate(df$steps, by=list(date=df$date), FUN=mean)
mediandf <- aggregate(df$steps, by=list(date=df$date), FUN=median)

names(meandf) <- c("day", "mean")
names(mediandf) <- c("day", "median")

ggplot(sumdf, aes(x=date, y=x)) + geom_bar(stat="identity") + ylab("Steps") + xlab("Date") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

3. Mean and median number of steps taken each day

Mean
```{r}
meandf
```

Median
```{r}
mediandf
```

4. Time series plot of the average number of steps taken

```{r}
medianIntervalDF <- aggregate(df$steps, by=list(interval=df$interval), FUN=median)
plot(medianIntervalDF$interval, medianIntervalDF$x, type = "l", ylab = "Mean steps", xlab = "")
```

5. The 5-minute interval that, on average, contains the maximum number of steps

```{r}
max(medianIntervalDF$x)
subset(medianIntervalDF, x == max(medianIntervalDF$x), select = interval)
```

6. Code to describe and show a strategy for imputing missing data

```{r}
datasetSummary <- summary(nadf)
datasetSummary[7,1]
```

```{r, warning=FALSE}
meanIntervalDF <- aggregate(df$steps, by=list(interval=df$interval), FUN=mean)
df <- merge(x = nadf, y = meanIntervalDF, by = "interval", all = TRUE)
df$steps[is.na(df$steps)] <- df$x
```

7. Histogram of the total number of steps taken each day after missing values are imputed

```{r}

sumdf <- aggregate(df$steps, by=list(date=df$date), FUN=sum)
meandf <- aggregate(df$steps, by=list(date=df$date), FUN=mean)
mediandf <- aggregate(df$steps, by=list(date=df$date), FUN=median)

names(meandf) <- c("day", "mean")
names(mediandf) <- c("day", "median")
```

Mean
```{r}
meandf
```

Median
```{r}
mediandf
```

8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
df$weekday  <- factor((weekdays(as.POSIXlt(df$date)) %in% c("poniedzia³ek", "wtorek", "œroda", "czwartek", "pi¹tek")), levels=c(FALSE, TRUE), labels=c('weekend', 'weekday'))

meanIntervalDF <- aggregate(df$steps, by=list(interval=df$interval, weekday=df$weekday), FUN=mean)

library(lattice)
xyplot(x~interval|weekday,meanIntervalDF,type='l',layout=c(1, 2))
```